---
title: "Create Test Data"
output: html_document
bibliography: ../mcat.bib
---

```{r}
library(usethis)
```


# Study Area
Data for the tests were taken from the Lower Pool 10 HREP. `\\mvrdfs\egis\Work\EMP\HREP_Projects\Lower_Pool10\MusselModel\Data`

# Test mussel data
`mcat/data-raw/lp10_all_individuals.csv`

Convert the individuals.csv file into a data frame
```{r}
individuals <- read.csv("Z:/Work/EMP/HREP_Projects/SteamboatSlough/Mussels/mcat/data-raw/lp10_all_individuals.csv", 
                        stringsAsFactors = FALSE)
```

Make this data available to the package. 
```{r eval=FALSE}
usethis::use_data(individuals, overwrite = TRUE)
```


# Create MCAT lookup tables
Use the tables in the MCAT report [@dunn2016] to populate the following tables:

* Listed species
* Tolerant species
* Tribe Lampsilini
* Tribes

Create a `.csv` file for each table and store in the `/data-raw` folder. 

Import the required MCAT tables
```{r}
listed <- read.csv("Z:/Work/EMP/HREP_Projects/SteamboatSlough/Mussels/mcat/data-raw/listed.csv", 
                   stringsAsFactors = FALSE)
tolerant <- read.csv("Z:/Work/EMP/HREP_Projects/SteamboatSlough/Mussels/mcat/data-raw/tolerant.csv", 
                     stringsAsFactors = FALSE)
lampsilini <- read.csv("Z:/Work/EMP/HREP_Projects/SteamboatSlough/Mussels/mcat/data-raw/lampsilini.csv", 
                     stringsAsFactors = FALSE)
tribe <- read.csv("Z:/Work/EMP/HREP_Projects/SteamboatSlough/Mussels/mcat/data-raw/tribe.csv", 
                     stringsAsFactors = FALSE)
```

Make this data available to the package. 
```{r eval=FALSE}
usethis::use_data(listed, overwrite = TRUE)
usethis::use_data(tolerant, overwrite = TRUE)
usethis::use_data(lampsilini, overwrite = TRUE)
usethis::use_data(tribe, overwrite = TRUE)
```

